\bf Excuse me, do you have a moment to talk about version control?

### 2017-07-06 README.Rmd
Typos
Clarify flow of time and development in first figure

The Git way is to track the evolution of `iris.R`, through a series of commits,
each equipped with an explanatory message. Figure \ref{fig:diy-vs-git}C depicts this linear, *in situ* development process. Figure \ref{fig:diy-vs-git}D shows the same history for a common collaborative Git workflow, where contributors work independently but sync regularly to a common version. Especially important 
versions get a human-readable tag, to signal a meaningful milestone. Yes, there 
is some pain in adopting the formalism of Git, but it is worth it.

@@

We've explored Git's powerful structure for file management, so where does GitHub fit in? [GitHub](https://github.com) complements Git by providing a slick user interface and distribution mechanism for Git repositories. Git is the software you will use locally to record changes to a set of files. GitHub is a hosting service that provides a Git-aware home for such projects on the internet. These relationships are shown in Figure \ref{fig:yours-theirs-github}. GitHub is like DropBox or Google Drive, but more structured, powerful, and programmatic.

The remote host acts as the clearinghouse for a Git-managed project. This allows
others to browse project files, explore their history, sync up with the current version, and perhaps even propose or make changes. GitHub's well-designed web interface is a dramatic improvement over traditional Unix Git servers. Many operations can be done entirely in the browser, including editing or adding files. It is easy to create a hyperlink to a specific file or location in a file, at a specific version, which can make meta-conversations about project code or reports much more productive. GitHub also offers granular control over who can see, edit, and administer a project.

@@

If I've convinced you to experiment with Git and GitHub, you need to do some initial setup. These first steps happen one or, for some steps, once per computer. This is excerpted from [Happy Git and GitHub for the useR](http://happygitwithr.com), which holds battle-tested instructions honed over several years in [STAT 545](http://stat545.com) at the University of British Columbia.

>>>>

The Git way is to track the evolution of `iris.R`, through a series of commits,
each equipped with an explanatory message. Figure \ref{fig:diy-vs-git}C depicts this linear, *in situ* development process, with development and time flowing from bottom to top. Figure \ref{fig:diy-vs-git}D shows the same history for a common collaborative Git workflow, where contributors work independently but sync regularly to a common version. Especially important versions get a human-readable tag, e.g., "draft-01", to signal a meaningful milestone. Yes, there is some pain in adopting the formalism of Git, but it is worth it.

@@

We've introduced Git's powerful structure for file management, so where does GitHub fit in? [GitHub](https://github.com) complements Git by providing a slick user interface and distribution mechanism for Git repositories. Git is the software you will use locally to record changes to a set of files. GitHub is a hosting service that provides a Git-aware home for such projects on the internet. These relationships are shown in Figure \ref{fig:yours-theirs-github}. GitHub is like DropBox or Google Drive, but more structured, powerful, and programmatic.

The remote host acts as the distributor for a Git-managed project. This allows
others to browse project files, explore their history, sync up with the current version, and perhaps even propose or make changes. GitHub's well-designed web interface is a dramatic improvement over traditional Unix Git servers. Many operations can be done entirely in the browser, including editing or adding files. It is easy to create a hyperlink to a specific file or location in a file, at a specific version, which can make meta-conversations about project code or reports much more productive. GitHub also offers granular control over who can see, edit, and administer a project.

@@

If I've convinced you to experiment with Git and GitHub, you need to do some initial setup. These first steps happen once or, for some steps, once per computer. This is excerpted from [Happy Git and GitHub for the useR](http://happygitwithr.com), which holds battle-tested instructions honed over several years in [STAT 545](http://stat545.com) at the University of British Columbia.

### 2017-07-06 README.tex
Typos
Clarify flow of time and development in first figure

The Git way is to track the evolution of \texttt{iris.R}, through a
series of commits, each equipped with an explanatory message. Figure
\ref{fig:diy-vs-git}C depicts this linear, \emph{in situ} development
process. Figure \ref{fig:diy-vs-git}D shows the same history for a
common collaborative Git workflow, where contributors work independently
but sync regularly to a common version. Especially important versions
get a human-readable tag, to signal a meaningful milestone. Yes, there
is some pain in adopting the formalism of Git, but it is worth it.

@@

We've explored Git's powerful structure for file management, so where
does GitHub fit in? \href{https://github.com}{GitHub} complements Git by
providing a slick user interface and distribution mechanism for Git
repositories. Git is the software you will use locally to record changes
to a set of files. GitHub is a hosting service that provides a Git-aware
home for such projects on the internet. These relationships are shown in
Figure \ref{fig:yours-theirs-github}. GitHub is like DropBox or Google
Drive, but more structured, powerful, and programmatic.

The remote host acts as the clearinghouse for a Git-managed project.
This allows others to browse project files, explore their history, sync
up with the current version, and perhaps even propose or make changes.
GitHub's well-designed web interface is a dramatic improvement over
traditional Unix Git servers. Many operations can be done entirely in
the browser, including editing or adding files. It is easy to create a
hyperlink to a specific file or location in a file, at a specific
version, which can make meta-conversations about project code or reports
much more productive. GitHub also offers granular control over who can
see, edit, and administer a project.

@@

If I've convinced you to experiment with Git and GitHub, you need to do
some initial setup. These first steps happen one or, for some steps,
once per computer. This is excerpted from
\href{http://happygitwithr.com}{Happy Git and GitHub for the useR},
which holds battle-tested instructions honed over several years in
\href{http://stat545.com}{STAT 545} at the University of British
Columbia.

>>>>

The Git way is to track the evolution of \texttt{iris.R}, through a
series of commits, each equipped with an explanatory message. Figure
\ref{fig:diy-vs-git}C depicts this linear, \emph{in situ} development
process, with development and time flowing from bottom to top. Figure
\ref{fig:diy-vs-git}D shows the same history for a common collaborative
Git workflow, where contributors work independently but sync regularly
to a common version. Especially important versions get a human-readable
tag, e.g., ``draft-01'', to signal a meaningful milestone. Yes, there is
some pain in adopting the formalism of Git, but it is worth it.

@@

We've introduced Git's powerful structure for file management, so where
does GitHub fit in? \href{https://github.com}{GitHub} complements Git by
providing a slick user interface and distribution mechanism for Git
repositories. Git is the software you will use locally to record changes
to a set of files. GitHub is a hosting service that provides a Git-aware
home for such projects on the internet. These relationships are shown in
Figure \ref{fig:yours-theirs-github}. GitHub is like DropBox or Google
Drive, but more structured, powerful, and programmatic.

The remote host acts as the distributor for a Git-managed project. This
allows others to browse project files, explore their history, sync up
with the current version, and perhaps even propose or make changes.
GitHub's well-designed web interface is a dramatic improvement over
traditional Unix Git servers. Many operations can be done entirely in
the browser, including editing or adding files. It is easy to create a
hyperlink to a specific file or location in a file, at a specific
version, which can make meta-conversations about project code or reports
much more productive. GitHub also offers granular control over who can
see, edit, and administer a project.

@@

If I've convinced you to experiment with Git and GitHub, you need to do
some initial setup. These first steps happen once or, for some steps,
once per computer. This is excerpted from
\href{http://happygitwithr.com}{Happy Git and GitHub for the useR},
which holds battle-tested instructions honed over several years in
\href{http://stat545.com}{STAT 545} at the University of British
Columbia.
